---
title: "Love vs extraterrestials"
author: "Graciela Orozco"
date: "Spring 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
help("m111surveyfa13")
mydata<-m111surveyfa13 <- na.omit(m111surveyfa13)
```

# A question of Belief

Your data is in the dataframe called "mydata" examine it in the environment tab  
do a variable analysis on the 3 Questions and then upload the appropriate Rmd template for this job.   
Also create an empty github repository called "Belief" and make it the remote repository for  
this assignment.  For each question supply graphical evidence, numerical summaries, an inferential test, and a conclusion.  When finished push your rmd file, your project file, and your knitted html file to your github repo.  Finally turn in to Canvas the link to your github repo.




# Your First Question  

### Do people who believe in Love at First sight also tend to believe in Life on other planets?

$H_0$ There is no relation between people who belive in love at first sight and those who belive in life on other planets.  
$H_A$ There is a correlation between people who belive in love at first sight and those who belive in life in other planets.
Graphic Display

```{r}
barchartGC(~love_first + extra_life,data=mydata, xlab='love at first sight')
```

People who believe in love at first sight also tend believe life on other planets. 


Numerical Summary

```{r}
table1 <- xtabs(~love_first + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```
There is not much of a difference between people who do believe in love at first sight and those who belive in life on other planets.

Inference

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

We fail to reject the null hypothesis. There is no evidence to support the contention of the relationship between love at first sight and extraterrestrial life. The p-value is bigger than 0.05.

# Your second Question  

### Is there a difference between boys and girls with respect to belief in life on other planets?

$H_0$ there is no difference between boys and girls with respect to belief in life on other planets  
$H_A$ there is a difference between boys and girls with respect to belief in life on other planets
 
Graphical Display 

```{r}
barchartGC(~extra_life + sex,data=mydata, xlab= 'believe in life on other planets')
```

There is no relationship between girls and boys with respect to their belief in life on other planets.


Numerical Summary

```{r}
table1 <- xtabs(~extra_life + sex, data=mydata)
rowPerc(table1)
colPerc(table1)
```
The summary shows a big difference between sex and their belief in life in other planets.

Inference

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
We reject the null hypothesis because the p-value is higher than 0.05.

# Your last Question   

### Is there a difference between boys and girls with respect to belief in love at First sight?

$H_0$ there is no relation between boys and girls with respect to belief in love at first sight   
$H_A$ there is relation between boys and girls with respect to belief in love at first sight 

Graphical Display
```{r}
barchartGC(~love_first + sex,data=mydata, xlab= 'believe in love at first life')
```

There is a relation between boys and girls with respect to their belief in love at first sight. 


Numerical Display
```{r}
table1 <- xtabs(~love_first + sex, data=mydata)
rowPerc(table1)
colPerc(table1)
```

There is a big similarity between boys and girls and their belief in love at first class.

Inference
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

We fail to reject the null hypothesis because the p-value is bigger than .05